\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System

### 2024-08-12 Paper/Paper.tex
Change folder structures; delete former trials; delete __init__.py

>>>>

	\section{Model Overview}

		Fig: OCT abnormities
		Fig: Fundus abnormities
		Fig: From Abnormity to Disease
		Fig: 3 parts
		Fig: fusion
		how to find grade

	\subsection{Abnormity Models}

		\subsubsection{Data Preparation}

			Table: Data source
			CycleGAN
				Fig: Intro
				Table: selection rates
				selection criteria
			Transformations

		\subsubsection{Training}

			intro to five-fold train/valid
			parameters used, hard device parameters

		\subsubsection{Results}

			For both OCT and Fundus:
				Fig: accuracy and loss over epochs
				Table: total accuracy and abnormities accuracies
				Table: numerical results for each abnormity
				Fig: t-SNE
				Fig: ROC for each abnormity

				Fig: GradCAM intro
				Fig: GradCAM example

	\subsection{Diagnosis Model}

		\subsubsection{Data Preparation}

			how to choose data (with an example)

		\subsubsection{Training}

			parameters used

		\subsubsection{Results}

			Do two models increase accuracy?
			Fig: accuracy and loss over epochs
			Table: total accuracy and disease accuracies
			Table: numerical results for each disease
			Fig: ROC for each disease

	\section{Conclusion}

		Comparison
		Strengths and weaknesses

	\section{Appendix}

		Google Image source links
		Table: OCT abnormities description
		Table: Fundus abnormities description
		APP/website description
